What public transit API logs tell us about travel flows

### 2016-01-14 paper.tex
Citations added

Another solution is to transform the visual representation. 
Flow maps \cite{phan2005flow} reduces clutter by rerouting the arrows to minimize intersection and obtain layouts that align with key geographic features like roads, rivers or coastlines. 
However, a certain degree of ambiguity is introduced to the visualization since the arrows do not depict actual paths of movement and maybe misleading to interpret.
A computationally cost effective alternative is to draw links as arcs instead of arrows \cite{chua2014flowsampler}.
Yet, this visual encoding may intensify the visual complexity of the representation.

>>>>

Another solution is to transform the visual representation. 
This can be achieved by bundling lines in close proximity to minimize intersections \cite{hurter2014bundled}.
Flow maps \cite{phan2005flow} follow the same principle to reduce clutter but yield layouts that align with key geographic features like roads, rivers or coastlines. 
However, a certain degree of ambiguity is introduced to the visualization by both techniques since the arrows do not depict actual paths of movement and maybe misleading to interpret.
Transition diagrams are a type of visulization that summarizes large numbers of trajectories while minimizing arbitary transformations to the layout \cite{andrienko2012visual}. 
The idea is to divide each trajectory into segments, so that movement on a path is approximated by a sequence of transitions between adjacent discrete locations. 
Locations are either predefined or obtained by various space partitioning algorithms. 
Arrows depict flows and are scaled to the aggregate number of transitions between pairs of adjacent locations. 
An advantage of this representation is that the topology of flows is captured as a directed graph, allowing for quantitative metrics like centrality to be computed and visually compared. 
Nonetheless, the solution requires substantial data processing prior to visualization and analysis.
A computationally cost effective alternative is to draw links as arcs instead of arrows \cite{chua2014flowsampler}.
Yet, this visual encoding may intensify the visual complexity of the representation.
